### 2019-04-10 README.Rmd
a few minor fixes
- get_ids should have ignore_case
- get_names does not need ignore_case
- update docs & spellcheck readme

The goal of `taxadb` is to provide *fast*, *consistent* access to taxonomic data, supporting commont tasks such as resolving taxonomic names to identifiers, looking up higher classification ranks of given species, or returning a list of all species below a given rank. These tasks are particularly common when synthesizing data across large species assemblies, such as combining occurrence records with trait records.

@@

Note that some names cannot be resolved to an identifier.  This can occur because of mis-spellings, non-standard formatting, or the use of a synonym not recognized by the naming provider.  Names that cannot be uniquely resolved because they are known synonyms of multiple different species will also return `NA`.  The `by_name` filtering functions can help us resolve this last case (see below).

@@

```{r}
most_synonyms <- taxa_tbl("col") %>% 
  group_by(acceptedNameUsageID) %>% 
  count(sort=TRUE)
most_synonyms
```
However, unlike the `by_*` functions which return convienent in-memory tables, this is still a remote connection.  This means that direct access using the `taxa_tbl()` function (or directly accessing the database connection using `td_connect()`) is more low-level and requires greater care.  For instance, we cannot just add a `%>% mutate(acceptedNameUsage = get_names(acceptedNameUsageID))` to the above, becuase `get_names` does not work on a remote collection.  Instead, we would first need to use a `collect()` to pull the summary table into memory.  Users familiar with remote databases in `dplyr` will find using `taxa_tbl()` directly to be convenient and fast, while other users may find the `by_*` approach to be more intuitive.

>>>>

The goal of `taxadb` is to provide *fast*, *consistent* access to taxonomic data, supporting common tasks such as resolving taxonomic names to identifiers, looking up higher classification ranks of given species, or returning a list of all species below a given rank. These tasks are particularly common when synthesizing data across large species assemblies, such as combining occurrence records with trait records.

@@

Note that some names cannot be resolved to an identifier.  This can occur because of miss-spellings, non-standard formatting, or the use of a synonym not recognized by the naming provider.  Names that cannot be uniquely resolved because they are known synonyms of multiple different species will also return `NA`.  The `by_name` filtering functions can help us resolve this last case (see below).

@@

```{r}
most_synonyms <- taxa_tbl("col") %>% 
  group_by(acceptedNameUsageID) %>% 
  count(sort=TRUE)
most_synonyms
```
However, unlike the `by_*` functions which return convenient in-memory tables, this is still a remote connection.  This means that direct access using the `taxa_tbl()` function (or directly accessing the database connection using `td_connect()`) is more low-level and requires greater care.  For instance, we cannot just add a `%>% mutate(acceptedNameUsage = get_names(acceptedNameUsageID))` to the above, because `get_names` does not work on a remote collection.  Instead, we would first need to use a `collect()` to pull the summary table into memory.  Users familiar with remote databases in `dplyr` will find using `taxa_tbl()` directly to be convenient and fast, while other users may find the `by_*` approach to be more intuitive.
